### 2012-07-10 docs/test_suite/test_suite.tex
add the test suite
remove references to fParallel

\begin{figure}[t]
\centering
\includegraphics[width=5.0in]{\suiteFigPath/testsuite}
\caption{\label{fig:test_suite_main} Main test suite results page.  Each 
row indicates a single test suite run, arranged by date, and each column
indicates a different test problem. }
\end{figure}

@@

An example of the {\tt main} block from {\tt Maestro-tests.ini} is:
\begin{lstlisting}
[main]
boxLibDir      = /home/zingale/tests/BoxLib/
sourceDir      = /home/zingale/tests/MAESTRO/
testTopDir     = /home/zingale/tests/
webTopDir      = /home/www/Maestro/test-suite/
compareToolDir = /home/zingale/tests/AmrPostprocessing/F_Src/
helmeosDir     = /home/zingale/tests/MAESTRO/fParallel/extern/EOS/helmeos/

sourceTree = fParallel

@@

The first group of options define the necessary paths.  Here, {\tt
  boxLibDir} points to the location of the \boxlib\ source, {\tt
  sourceDir} points to the top-level \maestro\ directory, which is
expected to contain the {\tt fParallel} subdirectories.  {\tt
  testTopDir} refers to the directory that the suite should use as its
root directory for running the tests and {\tt webTopDir} is the
directory in which to place the web output.  The {\tt fcompare.f90}
comparison tool source is expected to be found in {\tt
  compareToolDir}.  Finally, {\tt helmeosDir} lists the path to the
{\tt helm\_table.dat} file used by the general stellar equation of
state.

Next, we set {\tt sourceTree} to {\tt fParallel}, indicating that
\maestro\ is built using the Fortran \boxlib\ framework.  This option
tells the test suite what build system to use.

@@

\begin{lstlisting}
[test2]
buildDir = fParallel/MAESTRO/TEST_PROBLEMS/test2/
inputFile = inputs_2d
aux1File = model.hse.cool.coulomb
needsHelmEOS = 1
dim = 2
doVis = 1
visVar = ``tfromp''
compileTest = 0 
restartTest = 0
useMPI = 0
\end{lstlisting}

>>>>

\begin{figure}[t]
\centering
\includegraphics[width=5.0in]{\suitefigpath/testsuite}
\caption{\label{fig:test_suite_main} Main test suite results page.  Each 
row indicates a single test suite run, arranged by date, and each column
indicates a different test problem. }
\end{figure}

@@

An example of the {\tt main} block from {\tt Maestro-tests.ini} is:
\begin{lstlisting}
[main]
boxLibDir      = /home/zingale/tests/BoxLib/
sourceDir      = /home/zingale/tests/MAESTRO/
testTopDir     = /home/zingale/tests/
webTopDir      = /home/www/Maestro/test-suite/
compareToolDir = /home/zingale/tests/AmrPostprocessing/F_Src/
helmeosDir     = /home/zingale/tests/MAESTRO/Microphysics/EOS/helmeos/

sourceTree = F_Src

@@

The first group of options define the necessary paths.  Here, {\tt
  boxLibDir} points to the location of the \boxlib\ source, {\tt
  sourceDir} points to the top-level \maestro\ directory.  {\tt
  testTopDir} refers to the directory that the suite should use as its
root directory for running the tests and {\tt webTopDir} is the
directory in which to place the web output.  The {\tt fcompare.f90}
comparison tool source is expected to be found in {\tt
  compareToolDir}.  Finally, {\tt helmeosDir} lists the path to the
{\tt helm\_table.dat} file used by the general stellar equation of
state.

Next, we set {\tt sourceTree} to {\tt F\_Src}, indicating that
\maestro\ is built using the Fortran \boxlib\ framework.  This option
tells the test suite what build system to use.

@@

\begin{lstlisting}
[test2]
buildDir = TEST_PROBLEMS/test2/
inputFile = inputs_2d
aux1File = model.hse.cool.coulomb
needsHelmEOS = 1
dim = 2
doVis = 1
visVar = ``tfromp''
compileTest = 0 
restartTest = 0
useMPI = 0
\end{lstlisting}
